Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-15 paper.tex
Update paper.tex

\begin{longtable}{|l|l|l|l|l|}
\hline
\textbf{Factor} & \textbf{H2O} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endfirsthead

\multicolumn{5}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endhead

\hline \multicolumn{5}{|r|}{\textit{Continued on next page}} \\
\hline
\endfoot

@@

\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API & User-friendly API with minimal coding & Python library with fairly intuitive API\\
\hline
\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc. & Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc. (no DNN) & Linear, Tree, Clustering - More limited and lightweight & Linear, LightGBM, Catboost, etc. & Linear, tree, SVM, etc. \\
\hline
\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited & Advanced (automatic) & Basic \\
\hline
\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
\textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
\hline
\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning & Automated & Automated \\
\hline
\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
\hline
\hline
\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) & Good (distributing computing) & Moderate \\
\hline
\textbf{Customization} & High & Moderate & High & Low-Moderate & Moderate & Moderate \\
\hline

@@

>>>>

\begin{longtable}{|l|l|l|l|l|l|l|}
\hline
\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endfirsthead

\multicolumn{7}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
\hline
\endhead

\hline \multicolumn{7}{|r|}{\textit{Continued on next page}} \\
\hline
\endfoot

@@

\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API & User-friendly API with minimal coding & Python library with fairly intuitive API\\
\hline
\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc. & Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc. (no DNN) & Linear, Tree, Clustering - More limited and lightweight & Linear, LightGBM, Catboost, etc. & Linear, tree, SVM, etc. \\
\hline
\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited & Advanced (automatic) & Basic \\
\hline
\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
\hline
\textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
\hline
\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning & Automated & Automated \\
\hline
\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
\hline
\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) & Good (distributing computing) & Moderate \\
\hline
\textbf{Customization} & High & Moderate & High & Low-Moderate & Moderate & Moderate \\
\hline

@@

Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency. Given the restricted nature of tabular data, there are some models that, in general, are less likely to perform well, thus running and training these models is frequently wasteful. Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases and give frameworks versatility. We hypothesized that using a combination of layered machine learning implementation in which we train a model to predict a basic framework's outputs and meta-feature extraction in which we accelerate the training process by reducing complicated data matrices to their measurable attributes would yield an equally versatile system that minimizes time spent on prediction while still maximizing accuracy and straightforward implementation in a medical context.
